Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-15 main.tex
table 2 3 4 done

\begin{table}[hp]
\centering
\caption{The top 3 genes with prognostic impact in HNSCC}% (ranked by Bonferroni-adjusted \textit{P} values}
\label{tab:newTable1}
\resizebox{\linewidth}{!}{% \textwidth
\begin{tabular}{|l|l|l|c|c|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{} &
  \multicolumn{2}{c|}{} &
  \multicolumn{2}{c|}{Kaplan-Meier survival} &
  \multicolumn{2}{c|}{Cox Univariate} &
  \multicolumn{2}{c|}{Cox Multivariate} \\ \cline{4-9} 
\multicolumn{1}{|c|}{\multirow{-2}{*}{Gene ID}} &
  \multicolumn{2}{c|}{\multirow{-2}{*}{Gene Description}} &
  \begin{tabular}[c]{@{}c@{}}FDR\\ \textit{P} value\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Bonferroni\\ \textit{P} value\end{tabular} &
  HR* &
  95\% CI &
  HR* &
  95\% CI \\ \hline
CAMK2N1 &
  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}calcium/calmodulin-\\ dependent protein\\ kinase II inhibitor 1\end{tabular}} &
  \num{2.9e-7} &
  0.002 &
  2.101 &
  1.572-2.809 &
  2.007 &
  1.490-2.704 \\ \hline
IL19 &
  \multicolumn{2}{l|} {interleukin 19} &
   \num{3.7e-7} &
   0.002 &
   0.472 &
   0.351-0.635 &
   0.459 &
   0.340-0.619 \\ \hline
FCGBP &
  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}Fc fragment of\\  IgG binding protein\end{tabular}} &
   \num{1.2e-6} &
   0.008 &
   0.484 &
   0.359-0.653 &
   0.496 &
   0.366-0.674 \\ \hline
\multicolumn{9}{|l|}{} \\
\multicolumn{9}{|l|}%{\multirow{-0}{*}
{\begin{tabular}[c]{@{}l@{}}
Selection criteria (fit all):\\
1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;\\
2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in TCGA cohort;\\
3) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in GSE65858 cohort
\end{tabular}
%}\\ % within \multirow
} \\ % within \multicolumn
\hline
\multicolumn{9}{|l|}{* Cox’s model: \textit{P} \textless 0.001} \\ \hline

@@

%\subsubsection{Figure 3:h}
\begin{figure}
    \centering
    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
%Y axis: multivariate hazard ratio from Cox proportional regression model.
%Dotted line: significant Bonferroni corrected \textit{P} value. 
%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
    This cohort has been applied for exploration of the candidate biomarkers.
    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
    Remarks:\\
    \textcolor{red}{Red spots}: $HR > 1.0$;
    \textcolor{green}{Green spots}: $HR < 1.0$;\\
    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
    Y-axis: HR of Cox proportional hazard regression model\\
    }
%\label{fig:figure3}
\label{fig:hazards3} %TCGA volcano
\end{figure}
% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.

@@

\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}=65y                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\ 

@@

                                        & 65y                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.391                                                                          & 1.025-1.888                                                                   & \textcolor{red}{0.034}                                                         \\ 

@@

\multirow{2}{*}{RNA-Seq}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\ 

@@

                                        & 65y                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.481                                & 1.087-2.018                                      & \textcolor{red}{0.013}                     \\ 

@@

>>>>

\begin{table}[hp]
\centering
\caption{The top 3 genes with prognostic impact in HNSCC}% (ranked by Bonferroni-adjusted \textit{P} values}
\label{tab:newTable1}
\resizebox{\linewidth}{!}{% \textwidth
\begin{tabular}{|l|l|l|c|c|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{} &
  \multicolumn{2}{c|}{} &
  \multicolumn{2}{c|}{Kaplan-Meier survival} &
  \multicolumn{2}{c|}{Cox Univariate} &
  \multicolumn{2}{c|}{Cox Multivariate} \\ \cline{4-9} 
\multicolumn{1}{|c|}{\multirow{-2}{*}{Gene ID}} &
  \multicolumn{2}{c|}{\multirow{-2}{*}{Gene Description}} &
  \begin{tabular}[c]{@{}c@{}}FDR\\ \textit{P} value\end{tabular} &
  \begin{tabular}[c]{@{}c@{}}Bonferroni\\ \textit{P} value\end{tabular} &
  HR* &
  95\% CI &
  HR* &
  95\% CI \\ \hline
CAMK2N1 &
  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}calcium/calmodulin-\\ dependent protein\\ kinase II inhibitor 1\end{tabular}} &
  \num{1.63e-5} & %2.9e-7} &
  0.002 &
  2.101 &
  1.572-2.809 &
  2.007 &
  1.490-2.704 \\ \hline
IL19 &
  \multicolumn{2}{l|} {interleukin 19} &
   \num{6.54e-6} & %3.7e-7} &
   0.002 &
   0.472 &
   0.351-0.635 &
   0.459 &
   0.340-0.619 \\ \hline
FCGBP &
  \multicolumn{2}{l|}{\begin{tabular}[c]{@{}l@{}}Fc fragment of\\  IgG binding protein\end{tabular}} &
   \num{4.83e-5} & %1.2e-6} &
   0.008 &
   0.484 &
   0.359-0.653 &
   0.496 &
   0.366-0.674 \\ \hline
\multicolumn{9}{|l|}{} \\
\multicolumn{9}{|l|}%{\multirow{-0}{*}
{\begin{tabular}[c]{@{}l@{}}
Selection criteria (fit all):\\
1) Kaplan-Meier Bonferroni-adjusted \textit{P} \textless 0.05;\\
2) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in TCGA cohort;\\
3) Cox’s univariate and multivariate HR \textgreater{}= 1.8 or \textless{}= 0.5 in GSE65858 cohort
\end{tabular}
%}\\ % within \multirow
} \\ % within \multicolumn
\hline
\multicolumn{9}{|l|}{* Cox’s model: \textit{P} \textless 0.001} \\ \hline

@@

%\subsubsection{Figure 3:h}
\begin{figure}
    \centering
    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
%Y axis: multivariate hazard ratio from Cox proportional regression model.
%Dotted line: significant Bonferroni corrected \textit{P} value. 
%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
    This cohort has been applied for exploration of the candidate biomarkers.
    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.5$.\\
    Remarks:\\
    \textcolor{red}{Red spots}: $HR > 1.0$;
    \textcolor{green}{Green spots}: $HR < 1.0$;\\
    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
    Y-axis: HR of Cox proportional hazard regression model\\
    }
%\label{fig:figure3}
\label{fig:hazards3} %TCGA volcano
\end{figure}
% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.

@@

\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\ 

@@

                                        & $>65y$                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.391                                                                          & 1.025-1.888                                                                   & \textcolor{red}{0.034}                                                         \\ 

@@

\multirow{2}{*}{Gene Expression}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                            \\ 

@@

                                        & $>65y$                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.481                                & 1.087-2.018                                      & \textcolor{red}{0.013}                     \\ 

@@

%\subsubsection{Table4/legend} new Table 4 for FCGBP
% \ref{table:table_FCGBP}
\caption{Univariate/multivariate Cox's proportional hazards regression analyses on OS time of FCGBP gene expression in HNSCC}
                                        & Male                                                                                & 1.157                                                                          & 0.843-1.587                                                                   & 0.367                                                                         & 1.196                                & 0.858-1.669                                      & 0.291                                      \\ 
\multirow{2}{*}{Age at diagnosis}       & {\cellcolor[rgb]{0.62,0.812,0.878}}$<=65y$                                             & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\ 
                                        & $>65y$                                                                                 & 1.329                                                                          & 0.990-1.784                                                                   & 0.058                                                                         & 1.372                                & 1.008-1.867                                      & \textcolor{red}{0.044}                     \\ 
                                        & T3+T4                                                                               & 1.409                                                                          & 1.028-1.931                                                                   & \textcolor{red}{0.033}                                                        & 2.207                                & 1.169-4.165                                      & \textcolor{red}{0.015}                     \\ 
                                        & N1-3                                                                                & 1.185                                                                          & 0.890-1.577                                                                   & 0.246                                                                         & 1.328                                & 0.927-1.902                                      & 0.122                                      \\ 
                                        & M1                                                                                  & 4.097                                                                          & 1.009-16.644                                                                  & \textcolor{red}{0.049}                                                        & 7.571                                & 1.645-34.846                                      & \textcolor{red}{0.009}                     \\ 
                                        & Stage III+IV                                                                        & 1.245                                                                          & 0.882-1.759                                                                   & 0.213                                                                         & 0.454                                & 0.211-0.976                                      & \textcolor{red}{0.043}                                      \\ 
                                        & Positive                                                                            & 1.591                                                                          & 1.155–2.191                                                                   & \textcolor{red}{0.004}                                                        & 1.598                                 & 1.156-2.21                                      & \textcolor{red}{0.005}                     \\ 
                                        & High                                                                                & 1.364                                                                          & 1.008-1.844                                                                   & \textcolor{red}{0.044}                                                        & 1.502                                 & 1.087-1.087                                      & \textcolor{red}{0.014}                     \\ 
\multirow{2}{*}{Gene Expression}                & {\cellcolor[rgb]{0.62,0.812,0.878}}Low                                              & {\cellcolor[rgb]{0.62,0.812,0.878}}1                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}                                           & {\cellcolor[rgb]{0.62,0.812,0.878}}1 & {\cellcolor[rgb]{0.62,0.812,0.878}}              & {\cellcolor[rgb]{0.62,0.812,0.878}}        \\ 
                                        & High                                                                                & 0.484                                                                          & 0.359-0.653                                                                   & \multicolumn{1}{c|}{\textcolor{red}{***}}                                     & \multicolumn{1}{l|}{0.496}           & 0.366-0.674                                      & \multicolumn{1}{c|}{\textcolor{red}{***}}  \\ 
\label{table:table_FCGBP}
